---
title: "Dependencies Data Analysis"
output: html_notebook
---

```{r}
library(tidyverse)

besu_deps_direct <- read.csv("Data/besu-21.10.6_dependencies_direct.txt", sep = " ", header = FALSE)
teku_deps_direct <- read.csv("Data/teku-22.1.0_dependencies_direct.txt", sep = " ", header = FALSE)

besu_deps_all <- read.csv("Data/besu-21.10.6_dependencies_all.txt", sep = ":", header = FALSE)
teku_deps_all <- read.csv("Data/teku-22.1.0_dependencies_all.txt", sep = ":", header = FALSE)

besu_deps_all_Jan2021 <- read.csv("Data/besu-20.10.4_dependencies_all.txt", sep = ":", header = FALSE)
teku_deps_all_Jan2021 <- read.csv("Data/teku-21.1.0_dependencies_all.txt", sep = ":", header = FALSE)

besu_deps_all_Jan2021_gav <- read.csv("Data/besu-20.10.4_dependencies_all_gav.txt", sep = ":", header = FALSE)
besu_deps_all_gav <- read.csv("Data/besu-21.10.6_dependencies_all_gav.txt", sep = ":", header = FALSE)

teku_deps_all_Jan2021_gav <- read.csv("Data/teku-21.1.0_dependencies_all_gav.txt", sep = ":", header = FALSE)
teku_deps_all_gav <- read.csv("Data/teku-22.1.0_dependencies_all_gav.txt", sep = ":", header = FALSE)
```

# Unique direct dependencies

```{r}
besu_deps_direct <- besu_deps_direct %>% 
  rename(Type =  V2, GA = V3) %>% 
  select(GA) %>% 
  distinct()
print("Unique direct dependencies (Besu):")
nrow(besu_deps_direct)

teku_deps_direct <- teku_deps_direct %>% 
  rename(Type = V2, GA = V3) %>% 
  select(GA) %>% 
  distinct()
print("Unique direct dependencies (Teku):")
nrow(teku_deps_direct)
```
# Common direct dependencies

```{r}
common_direct <- inner_join(besu_deps_direct, teku_deps_direct, by = "GA")
print("Common direct dependencies:")
nrow(common_direct)
```

# Unique transitive dependencies

```{r}
# Besu
besu_deps_all <- besu_deps_all %>% 
  rename(G = V1, A = V2) %>% 
  mutate(GA = paste(G,A,sep = ":"))

besu_ga_direct <- besu_deps_direct %>% 
  mutate(GA = str_sub(GA, 2, nchar(GA) - 1))

besu_ga_all <- besu_deps_all %>% 
  select(GA) %>% 
  mutate(GA = str_sub(GA, 2, nchar(GA)))

besu_deps_transitive <- setdiff(besu_ga_all, besu_ga_direct)

print("Unique transitive dependencies (Besu):")
nrow(besu_deps_transitive)

# Teku
teku_deps_all <- teku_deps_all %>% 
  rename(G = V1, A = V2) %>% 
  mutate(GA = paste(G,A,sep = ":"))

teku_ga_direct <- teku_deps_direct %>% 
  mutate(GA = str_sub(GA, 2, nchar(GA) - 1))

teku_ga_all <- teku_deps_all %>% 
  select(GA) %>% 
  mutate(GA = str_sub(GA, 2, nchar(GA)))

teku_deps_transitive <- setdiff(teku_ga_all, teku_ga_direct)

print("Unique transitive dependencies (Teku):")
nrow(teku_deps_transitive)
```

# Common transitive dependencies

```{r}
common_transitive <- inner_join(besu_deps_transitive, teku_deps_transitive, by = "GA")
print("Common transitive dependencies:")
nrow(common_transitive)
```


# Unique third-party dependencies

```{r}
besu_ga_tp <- besu_deps_all %>%
  filter(!str_detect(G, 'project-'))

teku_ga_tp <- teku_deps_all %>%
  filter(!str_detect(G, 'project-'))
```

# Common third-party dependencies

```{r}
common_tp <- inner_join(besu_ga_tp, teku_ga_tp, by = "GA")
print("Common third-party dependencies:")
nrow(common_tp)
```
# Unique third-party suppliers

```{r}
besu_suppliers_all <- besu_deps_all %>%
  select(G) %>% 
  distinct()

teku_suppliers_all <- teku_deps_all %>%
  select(G) %>% 
  distinct()
```

# Common third-party suppliers

```{r}
common_suppliers <- inner_join(besu_suppliers_all, teku_suppliers_all, by = "G")
print("Common third-party suppliers:")
nrow(common_suppliers)
```

# Dependencies introduced in 2021

```{r}
besu_deps_all_Jan2021 <- besu_deps_all_Jan2021 %>% 
  rename(G = V1, A = V2) %>% 
  mutate(GA = paste(G,A,sep = ":")) %>% 
  select(GA)

besu_deps_all_Jan2022 <- besu_deps_all %>% 
  select(GA)

besu_deps_all_introduced <- setdiff(besu_deps_all_Jan2022, besu_deps_all_Jan2021)

print("Dependencies introduced in 2021 (Besu):")
nrow(besu_deps_all_introduced)

teku_deps_all_Jan2021 <- teku_deps_all_Jan2021 %>% 
  rename(G = V1, A = V2) %>% 
  mutate(GA = paste(G,A,sep = ":")) %>% 
  select(GA)

teku_deps_all_Jan2022 <- teku_deps_all %>% 
  select(GA)

teku_deps_all_introduced <- setdiff(teku_deps_all_Jan2022, teku_deps_all_Jan2021)

print("Dependencies introduced in 2021 (Teku):")
nrow(teku_deps_all_introduced)
```

# Common dependencies introduced in 2021
```{r}
common_deps_all_introduced <- inner_join(besu_deps_all_introduced, teku_deps_all_introduced, by = "GA")
print("Common dependencies introduced in 2021:")
nrow(common_deps_all_introduced)
```

# Dependencies modified in 2021

```{r}
# Besu
besu_Jan2022 <- besu_deps_all_gav %>%
  mutate(TMP = str_split_fixed(V2, " -> ", 2)[, 2]) %>%
  mutate(V2 = str_split_fixed(V2, " -> ", 2)[, 1]) %>%
  filter(!str_detect(V3, '->')) %>%
  mutate(V = paste(V3, TMP, sep = "")) %>%
  rename(G = V1, A = V2) %>%
  select(G, A, V) %>%
  mutate(GA = paste(G, A, sep = ":")) %>%
  mutate(GAV = paste(GA, V, sep = ":")) %>% 
  select(GA, GAV) %>% 
  mutate(Date = "Jan2022")

besu_Jan2021 <- besu_deps_all_Jan2021_gav %>%
  mutate(TMP = str_split_fixed(V2, " -> ", 2)[, 2]) %>%
  mutate(V2 = str_split_fixed(V2, " -> ", 2)[, 1]) %>%
  filter(!str_detect(V3, '->')) %>%
  mutate(V = paste(V3, TMP, sep = "")) %>%
  rename(G = V1, A = V2) %>%
  select(G, A, V) %>%
  mutate(GA = paste(G, A, sep = ":")) %>%
  mutate(GAV = paste(GA, V, sep = ":")) %>% 
  select(GA, GAV) %>% 
  mutate(Date = "Jan2021")

besu_join <- inner_join(besu_Jan2022, besu_Jan2021, by = "GA")

besu_deps_modified <- besu_join %>% 
  filter(GAV.x != GAV.y) %>%
  select(GA) %>% 
  distinct()

print("Dependencies modified in 2021 (Besu):")
nrow(besu_deps_modified)

besu_deps_intersection <- besu_join %>% 
  select(GA) %>% 
  distinct()

print("Dependencies in both versions (Besu):")
nrow(besu_deps_intersection)


# Teku
teku_Jan2022 <- teku_deps_all_gav %>%
  mutate(TMP = str_split_fixed(V2, " -> ", 2)[, 2]) %>%
  mutate(V2 = str_split_fixed(V2, " -> ", 2)[, 1]) %>%
  filter(!str_detect(V3, '->')) %>%
  mutate(V = paste(V3, TMP, sep = "")) %>%
  rename(G = V1, A = V2) %>%
  select(G, A, V) %>%
  mutate(GA = paste(G, A, sep = ":")) %>%
  mutate(GAV = paste(GA, V, sep = ":")) %>% 
  select(GA, GAV) %>% 
  mutate(Date = "Jan2022")

teku_Jan2021 <- teku_deps_all_Jan2021_gav %>%
  mutate(TMP = str_split_fixed(V2, " -> ", 2)[, 2]) %>%
  mutate(V2 = str_split_fixed(V2, " -> ", 2)[, 1]) %>%
  filter(!str_detect(V3, '->')) %>%
  mutate(V = paste(V3, TMP, sep = "")) %>%
  rename(G = V1, A = V2) %>%
  select(G, A, V) %>%
  mutate(GA = paste(G, A, sep = ":")) %>%
  mutate(GAV = paste(GA, V, sep = ":")) %>% 
  select(GA, GAV) %>% 
  mutate(Date = "Jan2021")

teku_join <- inner_join(teku_Jan2022, teku_Jan2021, by = "GA")

teku_deps_modified <- teku_join %>% 
  filter(GAV.x != GAV.y) %>%
  select(GA) %>% 
  distinct()

print("Dependencies modified in 2021 (Teku):")
nrow(teku_deps_modified)

teku_deps_intersection <- teku_join %>% 
  select(GA) %>% 
  distinct()

print("Dependencies in both versions (Teku):")
nrow(teku_deps_intersection)
```

# Common dependencies modified in 2021
```{r}
common_modified <- inner_join(besu_deps_modified, teku_deps_modified, by = "GA")
print("Common dependencies modified in 2021:")
nrow(common_modified)
```